Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-06 PaperBCJ.tex
Modificacion tablas

To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.\\

@@

\begin{table}[h!]
\centering
\begin{tabular}{| c | c | c | c | c |} 
 \hline
 Phase & Train & Validation & Test & Total \\ [1ex] 
 \hline
 Maize & 25695 & 8325 & 200 & 34220  \\ 
 Weed & 8560 & 2000 & 200 & 10760\\ 
 \hline
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

@@

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
  Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
  Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:2}
\end{table}

@@

\begin{table}[h!]
\centering
\begin{tabular}{|l c c |} 
 \hline
 Parameters & cNET 16 filters & cNET 64 filters \\ [0.75ex] 
 \hline
 Number of parameters & 1651376 & 6421568 \\ 
 Iterations & 9000 & 9000  \\ 
  Accuracy(\%) & 97.26 & 96.40  \\
  Loss(\%) & 8.39 & 14.48  \\ [1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:3}
\end{table}

@@

@@

@@

The before pictures shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\

@@

For this stage, we considered an extra dataset with 200 images of maize plants in stage of V3-V7 and 203 images of weed, obtained in maize crops, the results were comparated between cNET with 64 and 16 filters in the Table \ref{table:4}.\\  
\begin{table}[h!]
\centering
\begin{tabular}{|l|c|c|p{2cm}|}  
 \hline
 \multicolumn{4}{ |c| }{GPU} \\
 \hline
   cNET & \% Accuracy Weed & \% Accuracy Maize  & Average time of classification   \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 2.34 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 951  $\mu$ s \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification \\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 51.6 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 17.23 ms \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{CPU Raspberry Pi 3} \\
 \hline
   & \% Accuracy Weed & \%Accuracy Maize  & Average time of classification\\ 
 \hline 
 64 Filters & 81.6 & 88.36 & 615 ms  \\ [0.75ex]
 \hline
 16 Filters & 85.71 & 87.13 & 161 s \\ [0.75ex]
  \hline
\end{tabular}
\caption{Test}
\label{table:4}
\end{table}

>>>>

It should be noted that we had manually labeled the samples in two classes, maize and grass, having no account that the images are not repeated. In the following image we present the final results of the processed images that conform the dataset.\\

@@

\begin{table}[h!]
\centering
\begin{tabular}{| c  c  c  c  c |} 
 \hline
 \textbf{Phase} & \textbf{Train} & \textbf{Validation} &\textbf{Test}  & \textbf{Total} \\ [1ex] 
 \hline
 Maize & 25695 & 8325 & 200 & 34220  \\ 
 Weed & 8560 & 2000 & 200 & 10760\\ 
 \hline
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

@@

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{potena2016fast}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. \\
\begin{table}[h!]
\centering
\begin{tabular}{|l c c c c|} 
 \hline
 \textbf{Parameters }& \textbf{LeNet} & \textbf{AlexNet} & \textbf{cNET} & \textbf{sNET} \\ [0.75ex] 
 \hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 3000 & 3000 \\ 
  Accuracy(\%) & 86.48 & 93.86 & 95.33 & 80.4 \\
  Loss(\%) & 32.80 & 15.32 & 13.72 & 15.32 \\ [1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:2}
\end{table}

@@

\begin{table}[h!]
\centering
\begin{tabular}{|l c c |} 
 \hline
 \textbf{Parameters} & \textbf{cNET 16 filters} & \textbf{cNET 64 filters} \\ [0.75ex] 
 \hline
 Number of parameters & 1651376 & 6421568 \\ 
 Iterations & 9000 & 9000  \\ 
  Accuracy(\%) & 97.26 & 96.40  \\
  Loss(\%) & 8.39 & 14.48  \\ [1ex] 
 \hline 
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:3}
\end{table}

@@

Once the network architecture was chosen, it is constituted as follows: the input, a 64x64 RGB image layer followed by a convolution layer which reduces the image by taking only its main characteristics, then a layer of pooling which finds the maximum values of the characteristics found in the previous layer, followed by a second convolution, and a second layer of pooling, and finally two layers of type fully connected, from which in the end we have the output representing the two classes established in this network.\\

@@

The follow picture shows the schematic of the cNET of 16 filters and its process of training.Note that by reducing the number of filters the network gained accuracy because it does not have so much data to process.\\

@@

@@

For this stage, we considered an extra dataset with 200 images of maize plants in stage of V3-V7 and 203 images of weed, obtained in maize crops, the results were comparated between cNET with 64 and 16 filters in the Table \ref{table:4}.\\  
\begin{table}[h!]
\centering
\begin{tabular}{|p{1.1cm}|p{1.9cm}|p{1.95cm}|p{2cm}|}  
 \hline
 \multicolumn{4}{ |c| }{\textbf{GPU}} \\
 \hline
   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 2.34 ms  \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 951  $\mu$s \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{\textbf{CPU}} \\
 \hline
   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\ 
 \hline 
 64 Filters & 95.05\% & 74.75\% & 51.6 ms  \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 17.23 ms \\ [0.75ex]
  \hline
 \multicolumn{4}{ |c| }{\textbf{CPU Raspberry Pi 3}} \\
 \hline
   \textbf{cNET} & \textbf{Accuracy Weed} & \textbf{Accuracy Maize} & \textbf{Average time of classification}   \\
 \hline 
 64 Filters & 95.05 \% & 74.75\% & 615 ms  \\ [0.75ex]
 \hline
 16 Filters & 94.55\% & 87.13\% & 161 ms \\ [0.75ex]
  \hline
\end{tabular}
\caption{Test}
\label{table:4}
\end{table}
